Who introduced the bug? The importance of the previous commit

### 2016-01-28 paperMSR.tex
Some changes in the text

In spite of some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}.Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. We think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code.

The image \ref{fig:1} shows a clear example of we understand as responsible to cause the bug. In the image we can see three different versions of the same file in the history of the control version used in the project. The left code \textit{(1)} was written to fix the bug inserted in the middle code \textit{(2)} and with the \textit{31f08423} as the id of change,the previous commit. The code in the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug. In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was. And, according to the description of the commit log that fix the bug  \ref{fig:2}, this previous commit is responsible due to used the variable as string when had to be used as in the rest of the code, like as boolean.

Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug. The bug fix commit log, \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware. This change done because of the new requirements in the version doesn't implicate that the previous commit was who inserted the bug.

We based on some reasons to suppose that the previous commit didn't insert the bug. But, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy. Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it. As a result, the software fails at this line. But in fact, the previous commit which wrote the called API is not responsible, due to the line did't contain any bug at the moment in which was written.

@@

The remainder of this paper is structured as follows. First, we present the motivations that support our study,  explaining the current body of knowleadge in section~\ref{sec:related}. Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applaying our approach to OpenStack in Section~\ref{sec:results}. Section~\ref{sec:discussion} discusses potential applications and improvements of our approach. Section~\ref{sec:threats} reports threats to validity. Finally, Section~\ref{sec:conclusions} concludes the article.

@@

Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue. In this case, the ticket was classified into the \textit{Undecided} group.
\subsection{Second Stage: Responsability of Previous Commit}
\label{sec:secondStage}
The next part is focusing on analyzing the previous commit in the \textit{Bug Report} group. For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and be sure that the lines was inserted/modified in the previous commit. This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.

>>>>

In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}. Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understandig the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.

The image \ref{fig:1} shows a clear example of we understand as responsible to cause the bug. In the image we can see three different versions of the same file in the history of the control version used in the project. The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit. The code on the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug. In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was. And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as boolean keeping the concordance with the rest of the code.

Whereas the image \ref{fig:3} shows a clear example of we understand as no responsible to cause the bug. In this example, the bug fix commit log \ref{fig:4}, describes that in the update of the version, the name of an argument changed causing the failure in the sofware. This change was done because of the new requirements in the version, and this doesn't implicate that the previous commit inserted the bug, because when the line involved in the fix-bug was inserted by first time, it doesn't contain any bug.

We based on some reasons such as the explained before to suppose that the previous commit didn't insert the bug. Thus, our main idea to support this is that in a project which is evolving continuously and where many different developers are working on, the code that before was correct, now could be buggy. Thinking in called APIs, in the moment that this called was written there wasn't any bug and the software works fine, but in the addition of a new feauture or an enhancement the called API should be changed to support this new characteristic, but it didn't it. As a result, the software fails at this line. But in fact, the previous commit which wrote the called API is not responsible, due to the line did't contain any bug at the moment in which was written.

@@

The remainder of this paper is structured as follows. First, we present the motivations that support our study,  explaining the current body of knowleadge in section~\ref{sec:related}. Then, Section~\ref{sec:methodology} describes the methodology used to identify the moment in which the bug was inserted in the source code, followed by the results obtained after applaying our approach to OpenStack in Section~\ref{sec:results}. Section~\ref{sec:discussion} answers the research question suggested in ~\ref{sec:introduction}discusses potential applications and improvements of our approach. Section~\ref{sec:threats} reports threats to validity. Finally, Section~\ref{sec:conclusions} concludes the article.

@@

Sometimes we were unable to answer all the questions due to having insufficient data or because of the complexity of the issue. In this case, the ticket was classified into the \textit{Undecided} group.
\subsection{Second Stage: Who caused the Bug?}
\label{sec:secondStage}
The next part is focusing on analyzing the previous commit in the \textit{Bug Report} group. For that, we had to analyze the lines involved in the bug fix, in the commit parent of the bug fix commit, and be sure that the lines was inserted/modified in the previous commit. This, way we can sure that the previous commit didn't copied any line that contained the bug, because in this case, the previous commit is not responsible to cause the bug.
